\large{\bf Looking forwards and backwards through locally regulated populations }

### 2022-11-17 forwards-and-backwards-161122.tex
Update on Overleaf.

    Similarly, 
    \begin{align*}
        f(x, \smooth{r}\eta(y)) - f(x, \smooth{r}\eta(x))
        &=
        (\smooth{r}\eta(y) - \smooth{r}\eta(x)) f'(x, \smooth{r}\eta(x))
        + \frac{1}{2} (\smooth{r}\eta(y) - \smooth{r}\eta(x))^2 f''(x, m)
    \end{align*}
    for some $\smooth{r}\eta(x) \le m \le \smooth{r}\eta(y)$,
    where $f'$ and $f''$ denote the first and second derivatives with respect to the second argument.
    So,
    the second term in~\eqref{eqn:q_bound_split} is bounded by
    \begin{align*}
        \|f'\|_\infty
        \left|
            \theta \int_{\IR^d}
                (\smooth{r}\eta(y) - \smooth{r}\eta(x))
            q_\theta(x, dy)
        \right|
        +
        \|f''\|_\infty
        \left|
            \theta \int_{\IR^d}
                (\smooth{r}\eta(y) - \smooth{r}\eta(x))^2
            q_\theta(x, dy)
        \right| .
    \end{align*}
    Therefore, it suffices to show that there is a $K < \infty$ such that
    for all $\eta \in \measures$ and $x \in \IR^d$,
    \begin{equation}
        \label{eqn:first_moment_rho}
        \left|\theta \int_{\IR^d}
            ( \smooth{r} \eta(y)-\smooth{r} \eta(x) )
        q_\theta(x,dy)\right|
        \leq K \smooth{\gamma} \eta(x)
    \end{equation}
    and
    \begin{equation}
        \label{eqn:second_moment_rho}
        \theta \int_{\IR^d}
                \left( \smooth{r} \eta(y) - \smooth{r} \eta(x) \right)^2
        q_\theta(x,dy)
        \leq K \left(\smooth{\gamma}\eta(x) \right)^2 .
    \end{equation}
    Note that the right hand side of each is the average density
    over a wider region (since $\epsilon_\gamma > \epsilon_r$).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\appendix
\section{Markov Mapping Theorem Applications}
    \label{sec: Markov Mapping Theorem Application}
\subsection{Markov Mapping Theorem Application on Generator $A^{\theta}$}\label{sec: Markov Mapping Theorem Application - Prelimit}

We now introduce some notations to simply our calculations. For $\xi=\sum \delta_{(x_i,u_i)}$, we write $\textbf{x}=(x_1,x_2,...), \textbf{u}=(u_1,u_2,...)$ to be the collections of particles locations and levels respectively. With this notation we will write $f(\xi), f(\textbf{x},\textbf{u})$ interchangeably. We write $\Gamma (d\textbf{u})$ as the probability kernel that corresponds to assigning each particle an i.i.d. uniform $[0,\lambda]$-level, i.e.
$$\int f(\textbf{x},\textbf{u})\Gamma (d\textbf{u})=\frac{1}{\lambda^{|\xi|}}\int_{[0,\lambda]^{|\xi|}}f(\textbf{x},\textbf{u})d\textbf{u},$$
and we denote
$$\hat{g}(x):=\frac{1}{\lambda}\int_{0}^{\lambda}g(x,u)du, ~~\hat{f}(\xi)=\int f(\xi) \Gamma (d\textbf{u})$$ 
to be the spatial test functions with averaged level. By independence of the levels of the particles we have that
$$\hat{f}(\xi)=\int \prod_{(x,u) \in \xi}g(x,u) \Gamma(d\textbf{u})=\prod_{(x,u)\in \xi}\frac{1}{\lambda}\int_{0}^{\lambda} g(x,u) du=\prod_{x_i \in \Xi}\hat{g}(x_i).$$ 
We will now apply Markov Mapping Theorem while keeping notations consistent to that introduced in Section A.5 in \cite{kurtz/rodrigues:2011} with the aid of Table \ref{Markov Mapping Theorem Notation Table}.
\begin{table}[h]
    \centering
    \begin{tabular}{c|c}
    Notation in \cite{kurtz/rodrigues:2011} & Notation in this paper \\
    \hline\\
      $S$   &  $\mathcal{M}(\IR^d \times [0, \lambda))$\\\\
       $S_0$  &  $\mathcal{M}(\IR^d)$\\\\
       $A$ & $A^{\theta}$\\\\
       $(X_t)_{t \geq 0}$ & $(\xi^{\theta}_t)_{t \geq 0}$\\\\
       $\mu_0$ & $\Xi^{\theta}_0 \in \mathcal{M}(\IR^d)$\\\\
       $\nu_0$ & $\xi^{\theta}_0 \in \mathcal{M}(\IR^d \times [0,\lambda])$\\\\
       $f(\xi)$ & $\prod_{(x,u) \in \xi} g(x,u)$\\\\
        $\gamma_M$ & $ \mathcal{M}(\IR^d \times [0, \lambda)) \ni \xi \to \frac{1}{\lambda}\sum_{(x,u) \in \xi, u < \lambda} \delta_{x} \in \mathcal{M}(\IR^d)$\\\\
       $\alpha_M$ & $ \alpha_M(\Xi,d \nu) =     \begin{cases}
      0 & \text{if } \sum_{(x,u) \in \nu, u < \lambda} \delta_x \neq \Xi\\
       \prod_{(u_i,x_i) \in \nu} \frac{1}{\lambda} \ind_{[0,\lambda]}du_i & \text{if } \sum_{(x,u) \in \nu, u < \lambda} \delta_x = \Xi,\\
    \end{cases} $\\
&      where $du_i$ is the standard Lebesgue measure.
    \end{tabular}
    \caption{Markov Mapping Theorem Correspondence}
    \label{Markov Mapping Theorem Notation Table}
\end{table}
\begin{remark}
Note that $\gamma,\alpha$ in \cite{kurtz/rodrigues:2011} is replaced with $\gamma_M,\alpha_M$ to avoid confusion with the $\gamma, \alpha$ used in previous sections.
\end{remark}
First of all, note that $\gamma_M$ is Borel-measurable and $\alpha_M$ is a transition function from $\mathcal{M}(\IR^d \times [0, \lambda))$ to $\mathcal{M}(\IR^d)$. More importantly, we have the following simplified expression for an integral against $\alpha_M$:
\int_{\mathcal{M}(\IR^d\times [0,\lambda])}A^{\theta}f(\nu)\alpha_M(\Xi,d\nu)= \int   A^{\theta}f(\textbf{x},\textbf{u})\Gamma(d\textbf{u}). 
As a result, we can establish that
\begin{aligned}
\alpha_M(\Xi,\gamma^{-1}(\Xi)) &= \int_{\nu \in \gamma^{-1}(y)}\alpha_M (\Xi,d\nu) \\
&= \int_{\nu \in \prod_{x_i \in \Xi} \{x_i\}\times [0,\lambda]}\alpha_M (\Xi,d\nu)\\
&= \prod_{x_i \in \Xi}\frac{1}{\lambda}\int_{0}^{\lambda} du_i =1
\end{aligned}
With the simplified integral, it now suffices to show that the Martingale Problem 
\begin{equation}\label{Markov Mapping Theorem Martingale Condition Simplified}
C = \left\{\left(\int   f(\textbf{x},\textbf{u})\Gamma(d\textbf{u}),\int   A^{\theta}f(\textbf{x},\textbf{u})\Gamma(d\textbf{u})\right)\right\}    
has a solution, i.e. the process
\begin{aligned}
M_t:=& \int   f(\textbf{x}_t,\textbf{u}_t)\Gamma(d\textbf{u})-\int   f(\textbf{x}_0,\textbf{u}_0)\Gamma(d\textbf{u})-\int_{0}^{t}\int   A^{\theta}f(\textbf{x}_s,\textbf{u}_s)\Gamma(d\textbf{u})ds\\
=&\hat{f}(\xi_t)-\hat{f}(\xi_0)-\int_{0}^{t}\int   A^{\theta}f(\xi_s)\Gamma(d\textbf{u})ds
\end{aligned}    
is a martingale.\\
Once we manage to solve the Martingale Problem \eqref{Markov Mapping Theorem Martingale Condition Simplified}, the Markov Mapping Theorem guarantees the following fact:
\begin{enumerate}
    \item $N_t:=    f(\xi_t)-   f(\xi_0)-\int_{0}^{t}  A^{\theta}f(\xi_s)ds$ is a martingale for all $f\in D(A^{\theta})$,
    \item The process $(\gamma_M \circ \xi^{\theta}_t)_{t \geq 0}:= \left(\frac{1}{\lambda}\sum_{(x,u)\in \xi^{\theta}_t, u < \lambda} \delta_x\right)_{t \geq 0}=(\Xi^{\theta}_t)_{t \geq 0}$ solves the Martingale Problem \eqref{Markov Mapping Theorem Martingale Condition Simplified}.
    \item $\mathbb{P}\{\xi^{\theta}_t \in B | \mathcal{F}^{\Xi^{\theta}}_t\}=\alpha_M(\Xi^{\theta}(t),\meanq), ~~~B \in \mathcal{B}(\mathcal{M}(\IR^d \times [0,\lambda])).$
\end{enumerate}
Note that in particular, the third statement is equivalent to the fact that conditioned on the spatial configuration $\Xi^{\theta}_t$, the levels of the particles must be i.i.d uniformly between $[0,\lambda]$. We may also express this condition through the following equation:
\begin{equation}\label{Markov Mapping Theorem Cox Condition}
\mathbb{E}\left[e^{-\int_{S \times [0,\lambda]} f(x,u) \xi^{\epsilon,\theta,\lambda}(dx \times du)}\bigg| \mathcal{F}^{\Xi^{\epsilon,N}}_t\right]=e^{-\int F^{\epsilon,\theta,\lambda}_f(x) \Xi^{\epsilon,\theta,\lambda}_t(dx)},
where 
$$F^{\epsilon,\theta,\lambda}_f(x):=-\lambda\log \left(\frac{1}{\lambda}\int_{0}^{\lambda}e^{-f(x,u)}du\right)=-\lambda\log \left(1-\frac{1}{\lambda}\int_{0}^{\lambda}(1-e^{-f(x,u)})du\right).$$

Therefore we only need to solve Martingale Problem \eqref{Markov Mapping Theorem Martingale Condition Simplified}.\\

The procedure to solve the Martingale Problem \eqref{Markov Mapping Theorem Martingale Condition Simplified} is rather standard and set out in \cite{kurtz/rodrigues:2011}, albeit we will face more technicalities for this setting. Recall that the lookdown generator of our spatial-level process satisfies
\begin{align}\label{Lookdown generator N lambda theta prelimit}
A^{\theta}f(\xi)=&f(\xi)\sum_{(x,u)\in\xi}2\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\times
\int_u^{
\lambda}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\IR^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
\xi },dy) \nonumber \\
& \qquad \qquad \qquad \qquad +\int_{\IR^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy)\Bigg)dv_1 \nonumber\\
&+f(\xi )\sum_{(x,u)\in\xi}\,\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)},
where $f(\xi) =\prod_{(x,u) \in \xi}g(x,u)$. 
For easier computation we break the generator into three parts, 
\begin{aligned}
A^{\theta,1}f(\xi)=&f(\xi)\sum_{(x,u)\in\xi}2\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\times
\int_u^{
\lambda}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\IR^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
\xi },dy)\Bigg)dv_1,\\
A^{\theta,2}f(\xi)=&f(\xi)\sum_{(x,u)\in\xi}2\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\times
\int_u^{
\lambda}\Bigg(\frac{1}{2}\int_{\IR^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy)\Bigg)dv_1,\\
A^{\theta,3}f(\xi)=&f(\xi )\sum_{(x,u)\in\xi}\,\left(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)},
\end{aligned}
such that 
$$A^{\theta}f(\xi)=A^{\theta,1}f(\xi)+A^{\theta,2}f(\xi)+A^{\theta,3}f(\xi).$$
We now calculate each generator evaluated under our probability kernel $\Gamma$.
\footnotesize 
&\int A^{\theta,1}f(\xi) \Gamma(d\mathbf{u})\\ &=\int \Bigg\{f(\xi)\sum_{(x,u)\in\xi}2\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)
\int_u^{
\lambda}\Bigg(\frac 12\frac{g(x,v_1)}{g(x,u)}\int_{\IR^d}(g(y,u)-g(x,u))q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
\xi },dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
&=\sum_{(x,u)\in\xi} \int \Bigg\{\frac{f(\xi)}{g(x,u)}2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi)
\int_u^{
\lambda}\Bigg(\frac 12 g(x,v_1)\int_{\IR^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
\xi },dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
&=\sum_{(x,u)\in\xi}\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\int_{0}^{\lambda}\left\{
\int_u^{
\lambda} g(x,v_1)dv_1\times \int_{\IR^d} (g(y,u)-g(x,u))q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
\xi },dy)\right\}du\\
&=\sum_{(x,u)\in\xi}\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i)\frac{1}{\lambda}\int_{\IR^d} \left\{\int_{0}^{\lambda}
\int_u^{
\lambda} g(x,v_1) (g(y,u)-g(x,u))dv_1du\right\}q^{\mathfrak{m}}_{\epsilon,\theta}(x,\bar{
\xi },dy)
\normalsize
For the second generator, we have
\footnotesize
&\int A^{\theta,2}f(\xi) \Gamma(d\mathbf{u})\\&=\int \Bigg\{f(\xi)\sum_{(x,u)\in\xi}2\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\times
\int_u^{
\lambda}\Bigg(\int_{\IR^d} \left(\frac{g(y,v_1)+g(x,v_1)}{2}-1\right)q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
&=\sum_{(x,u)\in\xi}\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\int \Bigg\{f(\xi)\times
\int_u^{
\lambda}\Bigg(\int_{\IR^d}\left(g(y,v_1)+g(x,v_1)-2\right)q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy)\Bigg)dv_1\Bigg\} \Gamma(d\mathbf{u})\\
&=\sum_{(x,u)\in\xi}\lambda^{-1}\theta\gamma^{\mathfrak{m}}_{\theta}(x,\Xi)\prod_{(x_i,u_i)\neq (x,u)}\hat{g}(x_i) \frac{1}{\lambda}\int_{\IR^d}\Bigg\{\int_{0}^{\lambda}
\int_u^{
\lambda}g(x,u) \left(g(y,v_1)+g(x,v_1)-2\right)dv_1 du\Bigg\} q^{\mathfrak{m}}_{\epsilon,\theta}(x,\Xi,dy).
\normalsize
For the third generator we have that 
 &\int A^{\theta,3}f(\xi)\Gamma(d\mathbf{u})\\&=\int f(\xi )\,\left(\lambda^{-1} \sum_{(x,u)\in\xi}\theta \gamma^{\mathfrak{m}}_{\theta}(x,\Xi) u^2 -b_{\theta}(x,\Xi)u\right)\frac {\partial_u g(x,u)}{g(x,u)}\Gamma(d\mathbf{u}) \\

>>>>

    Similarly, 
    \begin{align*}
        f(x, \smooth{r}\eta(y)) - f(x, \smooth{r}\eta(x))
        &=
        (\smooth{r}\eta(y) - \smooth{r}\eta(x)) f'(x, \smooth{r}\eta(x))
        + \frac{1}{2} (\smooth{r}\eta(y) - \smooth{r}\eta(x))^2 f''(x, m)
    \end{align*}
    for some $\smooth{r}\eta(x) \le m \le \smooth{r}\eta(y)$,
    where $f'$ and $f''$ denote the first and second derivatives with respect to the second argument.
    So,
    the second term in~\eqref{eqn:q_bound_split} is bounded by
    \begin{align*}
        \|f'\|_\infty
            \theta \int_{\IR^d}
               \left| (\smooth{r}\eta(y) - \smooth{r}\eta(x))
               \right|
            q_\theta(x, dy)
        +
        \|f''\|_\infty
        \left|
            \theta \int_{\IR^d}
                (\smooth{r}\eta(y) - \smooth{r}\eta(x))^2
            q_\theta(x, dy)
        \right| .
    \end{align*}
    Therefore, it suffices to show that there is a $K < \infty$ such that
    for all $\eta \in \measures$ and $x \in \IR^d$,
    \begin{equation}
        \label{eqn:first_moment_rho}
        \theta \int_{\IR^d}
            \left|( \smooth{r} \eta(y)-\smooth{r} \eta(x) )\right|
        q_\theta(x,dy)
        \leq K \smooth{\gamma} \eta(x)
    \end{equation}
    and
    \begin{equation}
        \label{eqn:second_moment_rho}
        \theta \int_{\IR^d}
                \left( \smooth{r} \eta(y) - \smooth{r} \eta(x) \right)^2
        q_\theta(x,dy)
        \leq K \left(\smooth{\gamma}\eta(x) \right)^2 .
    \end{equation}
    Note that the right hand side of each is the average density
    over a wider region (since $\epsilon_\gamma > \epsilon_r$).
    Furthermore,
    applying Jensen's inequality on the function
    $\left|( \smooth{r} \eta(y)-\smooth{r} \eta(x) )\right|^2$,
    one can bound the first moment directly from estimates of the second moment.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\appendix

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Results on Lookdown Representations}
    \label{sec: Markov Mapping Theorem Application}
\subsection{Generators for the spatial processes}
Before defining the generator of the lookdown representations, 
we recall the generator of the spatial processes.

We first define our pre-limit
$(\eta^{N}(t))_{t>0}$ as a solution
to a Martingale Problem
with generator $\Pgen^{N}$.

\begin{definition}
    \label{def2: MP definition of pre-limit}
Let $F \in \mathcal{C}^{2}(\IR)$ and $f \in \mathcal{C}_{0}(\IR^d)$.
We define $\Pgen^N$ to be a generator
acting on test functions of the form
$F_f(\eta):=F (\langle f, \eta \rangle)$
such that 
\begin{equation}
\begin{aligned}
\Pgen^{N} F_f(\eta):=& \int_{\IR^d} \theta\gamma(x, \eta) \left\{\int_{\IR^d} \left\{F(\langle f, \eta \rangle + f(y)/N )-F(\langle f, \eta \rangle )\right\}r(y, \eta)q_{\theta}(x,dy)\right\}N\eta(dx)\\
&+\int_{\IR^d} \theta \mu(x, \eta) \left\{F(\langle f, \eta \rangle - f(x)/N )-F(\langle f, \eta \rangle )\right\}N\eta(dx).
\end{aligned}    
\end{equation}
In this case, our pre-limit model $(\eta^{N}(t))_{t \geq 0}$ is the solution to the Martingale Problem $(\Pgen^{N}, \eta_0)$, i.e. 
for all $F \in \mathcal{C}^{2}(\IR)$
and $f \in \mathcal{C}_{0}(\IR^d)$,
$$M_t:=F_f(\eta^{N}_t)-F_f(\eta_0)
-\int_{0}^{t}\Pgen^{N}F_f(\eta^{N}_s)ds$$
is a martingale, and the initial condition is distributed as a Poisson measure with mean measure $\eta_0$.
\end{definition}

We now write the candidate generator for the limiting object.

\begin{definition}
    \label{def2: MP definition of limit}
Let $F \in \mathcal{C}^{2}(\IR)$ and $f \in \mathcal{C}_{0}(\IR^d)$.
We define $\Pgen$ to be a generator
acting on test functions of the form
$F_f(\eta):=F (\langle f, \eta \rangle)$
such that 
\begin{equation}
    \label{eq: Limit Generator Definition}
\begin{aligned}
\Pgen^{\infty} F_f(\eta):=& F'(\langle f, \eta \rangle)
                   \times \left\{
                   \big\langle
                        \gamma(x, \smooth{\gamma} \eta(x))
                            \mathcal{B}\left(
                            f(\cdot) r(\cdot, \smooth{r} \eta(\cdot))
                            \right)(x)
                    +
                    f(x)
                        F(x, \smooth{F} \eta(x)),
                        \eta(dx)
                    \big\rangle
                   \right\}\\
                &+ \alpha F''(\langle f, \eta \rangle)
                  \times \left\{
                  \big\langle
                    \gamma \left( x, \eta \right)
                    r\left(x,\eta \right)
                    f^2(x),
                    \eta (dx)
                    \big\rangle 
                  \right\}.
\end{aligned}    
\end{equation}
We define $(\eta^{\infty}(t))_{t \geq 0}$ to be the solution to the Martingale Problem $(\Pgen^{\infty}, \eta_0)$, i.e. 
for all $F \in \mathcal{C}^{2}(\IR)$
and $f \in \mathcal{C}_{0}(\IR^d)$,
$$M_t:=F_f(\eta^{\infty}_t)-F_f(\eta_0)
-\int_{0}^{t}\Pgen^{\infty}F_f(\eta^{\infty}_s)ds$$
is a martingale, with initial condition distributed as a Poisson measure with mean measure $\eta_0$.
\end{definition}

\subsubsection{Convergence of the Generators for the Spatial Models}

Here, just as a sanity check, 
we make sure that the limiting generator is indeed the limit of the generators.

\begin{lemma}[Identifying the limit as a solution to the martingale problem]
    \label{lem:limit_mgale}
As $N \to \infty$,
$(\eta^{N}_t)_{t \geq 0}$ converges in $\mathcal{D}_{[0,\infty)}(\mathcal{M}_f(\IR^d))$
to $(\eta^{N}(t))_{t \geq 0}$.
\end{lemma}
\begin{proof}
We use Theorem 4.8.10 in \cite{EK}.
First of all, the set of functions
$\{F_f(\eta):= F(\langle f, \eta \rangle ),~
F \in \mathcal{C}^{2}(\IR), ~
f \in \mathcal{C}_{0}(\IR^d)\}$
is a dense and convergence-determining 
subset of functions in $\mathcal{M}_f(\IR^d)$.
Therefore, it suffices to show that for any $t>0$,
\begin{equation}
    \label{eq: Convergence Condition}
\lim_{N \to \infty}
\mathbb{E}\left[
\left(
F_f(\eta^{N}_{t+\tau})-F_f(\eta^{N}_t)
-\int_{t}^{t+\tau}\Pgen^{\infty}F_f(\eta^{N}_s)ds
\right)
\prod_{i=1}^{k}\langle h_i,\eta^{N}_{t_i} \rangle
\right]=0
\end{equation}
for all $k\geq 0$, $0\leq t_1<t_2<...,t_k \leq t < t+\tau$,
and $h_1,...,h_k \in \mathcal{C}_{0}(\IR^d)$.

As $N\to \infty$, 
$\theta/N \to \alpha$, 
$\theta/N^2 \to 0$,
and 
$$\int_{\IR^d} f^m(y) r(y,\eta) q_{\theta}(x,dy) \to f^m(x)r(x, \eta)$$
for $m=2,3$,
the third term in Equation \eqref{eq: Pre-Limit Generator Expanded} vanishes
while the second term converges to
that of Equation \eqref{eq: Limit Generator Definition}.
Furthermore,
$\mu(x,\eta) = r(x,\eta)\gamma(x,\eta)-\frac{1}{\theta}F(x,\eta) \to r(x,\eta)\gamma(x,\eta),$
so $f^2(x)\mu(x,\eta) \to r(x,\eta)\gamma(x,\eta) f^2(x)$.

\subsection{Generator of Lookdown Representations}

We now define the generator of the lookdown representations.
\begin{definition}[Martingale Problem Characterisation]
    \label{defn:lookdown_mgale}
For given positive values of $N$ and $\theta$
and $\lp_0 \in \mathcal{M}_F(\IR^d \times [0,N])$,
we define $(\lp^{N}_t)_{t \geq 0}$
to be the unique solution to the martingale problem
with initial condition $\lp_0$ and generator $A^{N}$ that satisfies
\begin{equation*}
\begin{split}
& A^{N}f(\lp ) \\
&\quad =
    f(\lp)
    \,\sum_{(x,u)\in \lp}\,
    2 \gamma(x, \eta)
    \Bigg\{ \frac{1}{2N} \int_u^N g(x,u_1) du_1
            \frac{
                \theta \int_{\IR^d}
                (g(y,u) - g(x,u))
                r(y, \eta) q_{\theta}(x,dy)
            }{ g(x,u) }
        \\
    &\qquad\qquad\qquad\qquad\qquad\qquad\qquad {} +
        \frac{\theta}{N} \int_u^N
        \int_{\IR^d}\left(
            \frac{ g(y,u_1) + g(x,u_1) }{ 2 } - 1
        \right)
        r(y, \eta) q_{\theta}(x,dy)
        du_1
    \Bigg\}\\
    &\qquad\qquad {} +
    f(\lp) \sum_{(x,u)\in\lp}\,
    \left(
        \frac{\theta}{N} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q_\theta(x, dy) u^2 -b_{\theta}(x,\eta)u
    \right)
    \frac{\partial_u g(x,u)}{g(x,u)}
    ,
\end{split}
\end{equation*}
for all smooth functions $g \in C^{2}_{0}(\IR^d)$,
where $f(\lp) = \prod_{(x, u) \in \lp} g(x, u)$ as defined in \eqref{eqn:test_functions},
and $\eta(\cdot) = \lp(\cdot \times [0, N]) / N$ is the scaled spatial pushforward of $\lp$,
as before.
\end{definition}

Similarly, 
we define the generator for the lookdown representation of the limiting spatial model.

\begin{definition}[Martingale Problem Characterisation, $N=\infty$]
    \label{defn:limiting_lookdown_mgale}
    For a given value of $\alpha \in [0, \infty)$,
    define the operator $A$ acting on test functions of the form
    $f(\xi) = \prod_{(x, u) \in \xi} g(x, u)$ with $g \in C_0^2(\IR^d \times [0, \infty))$
    and for which there exists a $u_0$ with $g(x, u) = 1$ for all $u > u_0$.
    Then, let $A f$ be
    \begin{equation}
    \begin{aligned} \label{eqn:limiting_lookdown_generator}
    A f(\lp)
    =&
        f(\lp)  \sum_{(x, u) \in \xi}
        \gamma(x, \eta)
            \frac{
                \DG(g(\cdot, u) r(\cdot, \eta))(x) - g(x,u) \DG r(x,\eta)
            }{
                g(x, u)
            }
    \\ &+
        f(\lp) \sum_{(x, u) \in \xi}
        2 \alpha \gamma(x,\Xi)r(x,\Xi) \int_u^\infty (g(x, u_1) - 1) du_1
    \\ &+
        f(\lp) \sum_{(x, u) \in \xi}
        \left(
            \alpha \gamma(x,\Xi)r(x,\Xi) u^2
            -
            \left\{
                \gamma(x, \eta) \DG r(x, \eta) + F(x, \eta)
            \right\} u
        \right)
        \frac{\partial_u g(x, u)}{ g(x,u) }  .
    \end{aligned}
    \end{equation}

    We say that a $\lpmeasures$-valued process $(\xi_t)_{t \ge 0}$
    is a solution to the $(A, \lp_0)$ martingale problem
    if it has initial distribution $\lp_0$
    and $f(\lp_t) - \int_0^t Af(\lp_s) ds$ is a martingale for all $f$
    as defined above.
\end{definition}

\subsubsection{Exact Statement on Markov Mapping Theorem results}

\begin{theorem}
\label{teo: lookdown on pre-limit well defined}
For each $N \in \mathbb{N}$,
there exists a solution $(\lp^N_t)_{t \geq 0}$ to the $(A^N, \lp^N_0)$ martingale problem.
Furthermore, if we define $\Xi^N_t = \frac{1}{N}\lp^N_t(dx \times [0,N])$ for $t \geq 0$,
then the pre-limiting model $(\eta^N_t(dx))_{t \geq 0}$ defined in Definition \ref{defn:mgale_construction}
and $(\Xi^N_t(dx))_{t \geq 0}$
shares the same distribution on $\mathcal{D}_{\mathcal{M}(\mathbb{R}^d)}[0,\infty)$.

Finally, 
for all $h\in \mathcal{C}(\mathbb{R}^d \times [0, N])$
\begin{equation}\label{Markov Mapping Theorem Cox Condition}
\mathbb{E}\left[e^{-\int_{\mathbb{R}^d \times [0,N]} h(x,u) \xi^{N}(dx \times du)}\bigg| \mathcal{F}^{\Xi^{N}}_t\right]=e^{-\int F^{N}_h(x) \Xi^{N}_t(dx)},
\end{equation}
where 
$$F^{\epsilon,\theta,N}_h(x):=-N\log \left(\frac{1}{N}\int_{0}^{N}e^{-h(x,u)}du\right)=-N\log \left(1-\frac{1}{N}\int_{0}^{N}(1-e^{-h(x,u)})du\right).$$
In other words,
conditioned on the spatial configuration $\Xi^N_t$,
the levels of the particles must be i.i.d uniformly between $[0,N]$.

The statement for the limiting case is similar,
with the only difference being the conditional distribution 
of the levels given the spatial projection.

\begin{theorem}
\label{teo: lookdown on limit well defined}
There exists a solution $(\lp_t)_{t \geq 0}$ to the $(A, \lp_0)$ martingale problem.

Furthermore, if we define $\Xi_t = \lim_{u_0 \to \infty} \frac{1}{u_0}\lp_t(dx \times [0,u_0])$,
then the limit model $(\eta_t(dx))_{t \geq 0}$ defined in Theorem \label{thm:nonlocal_convergence}
and $(\Xi_t(dx))_{t \geq 0}$
shares the same distribution on $\mathcal{D}_{\mathcal{M}(\mathbb{R}^d)}[0,\infty)$.

Finally, 
for all $h\in \mathcal{C}(\mathbb{R}^d)$ and for all $K>0$,
\begin{equation}\label{Markov Mapping Theorem Cox Condition limit}
\mathbb{E}\left[e^{-\int_{\mathbb{R}^d \times [0,K]} h(x) \xi(dx \times du)}\bigg| \mathcal{F}^{\Xi}_t\right]=e^{- K \int_{\mathbb{R^d}}(1-e^{h(x)}) \Xi_t(dx)}.
\end{equation}
In other words,
conditionally on $(\Xi_s)_{0\leq s \leq t}$
for each $s \in[0,t]$,
$\xi_s$ is conditionally Poisson with Cox measure $\Xi_s(dx) \times du$.
\end{theorem}

\subsection{Markov Mapping Theorem Application on Generator $A^{N}$}\label{sec: Markov Mapping Theorem Application - Prelimit}

We now introduce some notations to simplify our calculations.
For a finite atomic measure $\xi=\sum \delta_{(x_i,u_i)} \in \mathcal{M}(\mathbb{R}^d \times [0,N])$,
we introduce the test functions
 $$f_g(\xi)= \prod_{(x_i,u_i)\in \xi} g(x_i,u_i) = \exp (\langle \log g, \xi \rangle),$$
 where $g \in \mathcal{C}(\mathbb{R}^d \times [0,\infty))$ and $g(x,u)=1$ for all $u \geq N$.

 To avoid any ambiguities in the proofs,
 we will strictly use the notation $\Xi^N$  
to represent the scaled push-forward measure of $\lp$,
i.e. $\Xi^N := \frac{1}{N}\sum_{(x,u) \in \lp} \delta_x$,
and only use $(\eta^N_t)_{t \geq 0}$
to refer to the PDE solutions defined in Definition  \ref{defn:mgale_construction}.

We also write $\textbf{x}=(x_1,x_2,...), \textbf{u}=(u_1,u_2,...)$ to be the collections of particles locations and levels respectively.
With this notation we will write $f_g(\xi), f_g(\textbf{x},\textbf{u})$ interchangeably.

We write $\Gamma^N (d\textbf{u})$ as the probability kernel
that corresponds to assigning each particle an i.i.d. uniform $[0,N]$-level, i.e.
$$\int f_g(\textbf{x},\textbf{u})\Gamma^N (d\textbf{u})=\frac{1}{N^{|\xi|}}\int_{[0,N]^{|\xi|}}f_g(\textbf{x},\textbf{u})d\textbf{u},$$
and we denote
$$\hat{g}(x):=\frac{1}{N}\int_{0}^{N}g(x,u)du,
 ~~\hat{f}_g(\xi)=\int f_g(\xi) \Gamma (d\textbf{u})$$ 
to be the spatial test functions with averaged level.
By independence of the levels of the particles,
 we have that
 \begin{align*}
\hat{f}_g(\xi)
=&\int \prod_{(x,u) \in \xi}g(x,u) \Gamma(d\textbf{u})\\
=&\prod_{(x,u)\in \xi}\frac{1}{N}\int_{0}^{N} g(x,u) du\\
=&\prod_{(x_i,u_i)\in \xi }\hat{g}(x_i)\\
=& \exp(N\log \hat{g},\Xi^N).
 \end{align*}

Furthermore,
when expressed as a function of $\Xi^N$ explicitly,
we use the notation $F_{\hat{g},N}(\Xi^N):=\hat{f}_g(\xi)$.
